\documentclass[a4paper,10pt]{article}
\usepackage[utf8x]{inputenc}

%opening
\title{Project Synopsis and Timeline}
\author{David Jinkins}

\begin{document}

\maketitle

\section{Project Synopsis}
Conspicuous consumption is a wasteful signal of wealth. Recent evidence on consumption habits in developing countries suggests that conspicuous consumption distortions may seriously harm the very poor.  A tax on visible goods has the potential to increase social welfare, but the welfare gains of such a tax hinge critically on how much people care about social status. My research suggests a method to estimate the importance of conspicuous consumption in a society from household budget data.  This sort of data is collected by most countries as it is important for calculating consumer price indexes.  Anecdotal evidence suggests that Chinese society places a high value on social status and engages heavily in conspicuous consumption.  I will use Chinese household budget data to evaluate this intuition empirically.  Since my baseline estimation is done on American data, this will allow me to compare the importance of conspicuous consumption in the United States and China.     

\section{Tentative Timeline}
\begin{description}
 \item [Pre-departure] Finalize model and estimation strategy, estimate on American data, determine what specific data I will be able to access in China (see proposal).  If some of the data are available before departure, clean and prepare so as not to waste time upon arrival. 
 \item [wk1] Arrive in Beijing, meet with host and other researchers. If necessary make initial visits to location of applicable data.
 \item [wk2] Clean-up data as needed, prepare for estimation.
 \item [wk3] Perform estimation.  Troubleshoot, address known estimation issues.
 \item [wk4] Begin write up of results.  Discuss results with researchers at CCER.
 \item [wk5] Put together a presentation, present where possible, get comments.
 \item [wk6] Continue presentations, address estimation issues as they are raised.
 \item [wk7] Final chance to make changes to estimation.
 \item [wk8] Finalize write-up.
\end{description}

\end{document}
