\documentclass[a4paper,10pt]{article}
%\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
%\usepackage{natbib}
\usepackage{fullpage}

%opening
\title{Biographical Sketch}
\author{David Jinkins}

\begin{document}

\maketitle

I am an American citizen.  I attended Sturgeon Bay High School in Sturgeon Bay, Wisconsin.  This is my first time applying for an EAPSI fellowship.  I heard about the program earlier this year from a professor.    
\section*{Academic Background}
I have a 2005 BA in Political Science from Carleton College in Northfield, Minnesota.  While at Carleton I spent one semester directly enrolled in the International Relations Department at Peking University, and I spent one summer interviewing unemployed workers in Manchuria.  My summer in Manchuria was funded with a Chang-Lan Fellowship.  In 2006 I received a Fulbright Fellowship to study Chinese migrants in Istanbul.  My host was Ahmed Icduygu of Koc University.  From 2007 to 2009, I was enrolled in the Economics masters program at National Taiwan University in Taipei, Taiwan.  My masters thesis advisor was Professor Hung-Ju Chen.  The thesis was a simple model of return migration governed by bounded rationality.  My studies in Taiwan were fully financed by a Taiwan Scholarship from the Taiwanese Ministry of Education.  I received my MA in Economics in the summer of 2009. Since then I have been enrolled in the Economics PHD program at Penn State University.  I passed my qualifying exams in Summer 2010.  In my second year empirical methods project, I estimated the marginal effect of an additional migrant on the level of bilateral trade between two countries.  My first two years at Penn State were funded by a departmental fellowship.  I am currently working as a research assistant for Professors Jonathan Eaton and Jim Tybout.           

\section*{Research Experience}
While in Taiwan, I was a research assistant for Assistant Professor Chun-Fang Chiang.  The project I worked on involved estimating learning behavior in hospital visits during the SARS epidemic of 2003.  We had access to an individual-level data set recording hospital visits, doctors seen, procedures carried out, medicines prescribed, etc.  This information was compiled from the databases of Taiwan's public health care system.  I wrote STATA do files for this project, and also counted articles mentioning SARS in various Taiwanese newspapers.

I am currently working as a research assistant on another learning project, this time using Colombian transactions-level trade data.  The basic idea is to model the matching process of Colombian exporters and American clients. In the model, each time a Colombian exporter meets a new American client, she learns more about demand for her product in the United States.  Since I started working on this project, the model has changed from discrete to continuous time.  I have rewritten much of the original MATLAB estimation code to reflect this change.  I have also implemented version control to track program changes and facilitate collaboration, and introduced parallel processing into the code for huge gains in evaluation time.  

\section*{International Experience}
I have lived in China (and Taiwan) for a cumulative total of four years.  I lived in Turkey for one year.  I can speak, read, and type in both Turkish and Chinese.  Most of my time abroad was in academic environments, and I am comfortable doing research in foreign countries.  I have a fair amount of experience navigating bureaucracy in Turkey and China (and the United States).  I also really enjoy living abroad.

\section*{Other Experience and Skills}
After graduating from college, I worked at an international freight forwarder in New York for a year.  It was a small company, so I was responsible for everything from calculating and sending out quotes to coordinating shipments and actually preparing bills of lading and letters of credit.  Some of the more interesting items I shipped were used school buses from the United States to West Africa and replacement parts for power plants in South Asia.  Although I was only at the company for one year, I learned about how different kinds of items are packed into containers, how shipping lines work, and the meaning of shipping terms like CIS and FOB.

I am proficient at writing code for computers in a number of languages.  I am comfortable using MATLAB, STATA, Mathematica, and git.  I can code in latex and html and I know some css.  As is true of any applied economics graduate student these days, I can understand and apply very abstract statistical models to actual data estimation.  My field courses last year were in game theory, trade, and development, so I know state-of-the-art research in these fields fairly well.  As I am sure my reference writers will attest, I am a hard worker.

\section*{Interest in EAPSI Fellowship}
The incredible growth and structural change seen in the last 30 years of China's history make it a great place to test economic theory.  Due to my understanding of Chinese language and culture, one of my comparative advantages as an applied economist is working in China with Chinese data.  An EAPSI fellowship will give me the opportunity to establish relationships with the top economic researchers in China, hopefully leading to research opportunities extending beyond Summer 2012.     

\section*{Working Papers}
\begin{itemize}
 \item Social Networks, Migrant Stocks, and Trade (with Gary Lyn) \emph{(Empirical Methods Project)}
 \item A Bridge goes Both Ways: A Two-Way Migration Model with Social Capital and Incomplete Information \emph{(Master's Thesis)}
\end{itemize}


\end{document}

